### 2023-04-18 manuscript.tex
update semantic seg 2d [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/b6e8bff54a82660f8e7c4a55245cf69efa6f4599.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/b6e8bff54a82660f8e7c4a55245cf69efa6f4599/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4737204064

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/5cb2675bca1cf03fae1df60e046267940cfb6684/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/5cb2675bca1cf03fae1df60e046267940cfb6684}{MMV-Lab/im2im-paper@5cb2675}
on April 6, 2023.

@@

Segmentation is a common image processing task, and can be considered as a special type of image-to-image transformation, where the generated images are segmentation masks. DL based methods have achieved huge success in 2D semantic segmentation in biomedical images. In this example, we demonstrated \emph{MMV\_Im2Im} on a pathology application to segment glands from hematoxylin and eosin (H\&E) stained tissue images from the 2015 Gland Segmentation challenge {[}\protect\hyperlink{ref-45Sirz1X}{29},\protect\hyperlink{ref-XAffSYIR}{30}{]}. Stain normalization is an important pre-processing step in order to develop models robust to stain variation and tissue variations. \emph{MMV\_Im2Im} included a classic stain normalization method {[}\protect\hyperlink{ref-tQhnZyjK}{31}{]} as a pre-processing step. The effect of stain normalization can be observed in Figure \ref{fig:2d_gland}-A and B. We trained a simple attention UNet model {[}\protect\hyperlink{ref-OCow1hly}{26}{]}. Evaluated on the two different hold-out test sets, the model achieved F1-score, 0.883 and 0.888 on test set A and test set B, respectively. The performance was competitive comparing to the methods reported in the challenge report {[}\protect\hyperlink{ref-XAffSYIR}{30}{]}, especially with much more consistent performance across the two different test sets. Example results can be found in Figure \ref{fig:2d_gland}-C.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/b6e8bff54a82660f8e7c4a55245cf69efa6f4599/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/b6e8bff54a82660f8e7c4a55245cf69efa6f4599}{MMV-Lab/im2im-paper@b6e8bff}
on April 18, 2023.

@@

Segmentation is a common image processing task, and can be considered as a special type of image-to-image transformation, where the generated images are segmentation masks. DL based methods have achieved huge success in 2D semantic segmentation in biomedical images. In this example, we demonstrated \emph{MMV\_Im2Im} on a pathology application to segment glands from hematoxylin and eosin (H\&E) stained tissue images from the 2015 Gland Segmentation challenge {[}\protect\hyperlink{ref-45Sirz1X}{29},\protect\hyperlink{ref-XAffSYIR}{30}{]}. Stain normalization is an important pre-processing step in order to develop models robust to stain variation and tissue variations. \emph{MMV\_Im2Im} included a classic stain normalization method {[}\protect\hyperlink{ref-tQhnZyjK}{31}{]} as a pre-processing step. The effect of stain normalization can be observed in Figure \ref{fig:2d_gland}-A and B. We trained a simple attention UNet model {[}\protect\hyperlink{ref-OCow1hly}{26}{]}. Evaluated on the two different hold-out test sets, the model achieved F1-score, 0.90 and 0.86 on test set A and test set B, respectively. The performance was competitive comparing to the methods reported in the challenge report {[}\protect\hyperlink{ref-XAffSYIR}{30}{]}, especially with much more consistent performance across the two different test sets. Example results can be found in Figure \ref{fig:2d_gland}-C.
